---
title: "Mastering Software Development R - Week 4 Project"
author: "Brandon"
date: "2021-11-06"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{test_vig}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)

```

## Introduction 

The R package **TestPackage** is set a tools to allow users to analyze and visualize data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System. 

The Fatality Analysis Reporting System is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.


## Summarizing Functions
The package contains one summary function that will take a vector of years as an argument, and return the total motor vehicle fatalities by month for those years.

```{r echo=TRUE, warning=FALSE, include=TRUE}
library(TestPackage)

#get summary data for 2014
sum_data <- TestPackage::fars_summarize_years(2014)

```

```{r echo=TRUE, include=TRUE}

#print summary data
sum_data

```


## Visualizing Functions
The package contains one visualizatin functions that allows users to choose one state and one year and plot that location of each fatility that occured in the state on a map of the state. 

```{r, echo=TRUE, include=TRUE}

#plot fatality data by state/year
fars_map_state(10, 2014)

```

